Naturalness in U(1) extensions of the MSSM

### 2014-11-11 paper/e6ssm-tuning-paper.tex
fix typo top --> to.

While this approach has many merits here will employ the traditional
measure of fine tuning because it is both simple to apply and easy top
compare with previous results due to it's widespread use.  Fortunately
the derivatives which appear in these tuning are also similar to the
Bayesian motivated measure so there should not be too large a discrepancy between the two approaches.

>>>>

While this approach has many merits here will employ the traditional
measure of fine tuning because it is both simple to apply and easy to
compare with previous results due to it's widespread use.  Fortunately
the derivatives which appear in these tuning are also similar to the
Bayesian motivated measure so there should not be too large a discrepancy between the two approaches.
